Women in Film

### 2017-07-17 draft_post.Rmd
Mmmmmmm, MOAR CLEANING

```{r pronoun_ratio, echo = FALSE, dependson="pronoun_bigrams", fig.width=8, fig.height=8}
pronoun_ratio <- pronoun_bigrams %>%
    count(word1, word2) %>%
    spread(word1, n, fill = 0) %>%
    mutate(total = he + she,
           he = (he + 1) / sum(he + 1),
           she = (she + 1) / sum(she + 1),
           logratio = log2(she / he)) %>%
    arrange(desc(logratio)) %>%
    filter(nchar(word2) > 2,
           !(word2 %in% c("door", "ad", "he", "1s", "lp",
                          "car", "himself", "pans", "dead", 
                          "queen", "back", "too", "were",
                          "doesn", "half")))

@@

There are dramatic differences in the kinds of words we see here. In movies, women are more likely to snuggle, giggle, squeal, and sob while men are more likely to gallop, shoot, howl, and kill. We see evidence here of the tropes and storytelling conventions that propel so many films, and how men, women, and their relationships are often portrayed.

@@

```{r, echo = FALSE, dependson="pronoun_ratio"}
example_text <- pronoun_ratio %>% 
    top_n(800, total) %>% 
    head(20) %>% 
    select(word = word2) %>%
    bind_rows(data_frame(word = c("cleans", "moans", "laughs", "twirls",
                                  "lingers", "bursts", "retreats", "answer",
                                  "creeps"))) %>%
    bind_rows(pronoun_ratio %>% 
                  top_n(800, total) %>% 
                  tail(20) %>% 
                  select(word = word2))

example_text
```

@@

There are some words that writers who are men and women are more likely to use, no matter what kind of character they are writing. In the upper right quadrant, we find the words that writers who are women are more likely to use. Writers who are women are more likely to write characters who sing, love, shift, sink into things, and burst into places. And lots of flinging! The lower left quadrant shows the words that writers who are men are more likely to use, for both male and female characters. Writers who are men are more likely to write characters who react, clutch, dive, shout, and emerge from places.

>>>>

```{r pronoun_ratio, echo = FALSE, dependson="pronoun_bigrams", fig.width=8, fig.height=8}
pronoun_ratio <- pronoun_bigrams %>%
    count(word1, word2) %>%
    spread(word1, n, fill = 0) %>%
    mutate(total = he + she,
           he = (he + 1) / sum(he + 1),
           she = (she + 1) / sum(she + 1),
           logratio = log2(she / he)) %>%
    arrange(desc(logratio)) %>%
    filter(nchar(word2) > 2,
           !(word2 %in% c("door", "ad", "he", "1s", "lp",
                          "car", "himself", "pans", "dead", 
                          "queen", "back", "too", "were",
                          "doesn", "half", "with", "been", 
                          "who", "she", "the", "very",
                          "and", "didn")))

@@

There are dramatic differences in the kinds of words we see here. In movies, women are more likely to snuggle, giggle, squeal, and sob while men are more likely to strap things on, gallop, shoot, howl, and kill. We see evidence here of the tropes and storytelling conventions that propel so many films, and how men, women, and their relationships are often portrayed.

@@

```{r, echo = FALSE, dependson="pronoun_ratio"}
example_words <- pronoun_ratio %>% 
    top_n(800, total) %>% 
    head(20) %>% 
    select(word = word2) %>%
    bind_rows(data_frame(word = c("cleans", "moans", "laughs", "twirls",
                                  "lingers", "bursts", "retreats", "answers",
                                  "creeps", "types", "attacks", "inhales",
                                  "stares", "grimaces", "suddenly", "stops",
                                  "ducks", "waits", "stomps", "remembers",
                                  "scrambles", "splashes", "jerks", "throws",
                                  "knows", "exhales", "coughs", "flops",
                                  "crouches", "staggers", "forgets", "slashes"))) %>%
    bind_rows(pronoun_ratio %>% 
                  top_n(800, total) %>% 
                  tail(20) %>% 
                  select(word = word2))

pronouns <- c(sample(c(" she", "She"), size = 36, replace = TRUE), 
              sample(c(" he", "He"), size = 36, replace = TRUE))

example_text <- example_words %>%
    mutate(pronoun = pronouns,
           phrase = str_c(pronoun, word, sep = " ")) %>%
    pull(phrase) %>%
    map_df(function(x) all_lines %>%
               filter(str_detect(text, x)) %>%
               sample_n(1) %>%
               select(text)) %>%
    bind_cols(example_words) %>%
    select(word, text)

write_csv(example_text, "./example_texts.csv")
```

@@

There are some words that writers who are men and women are more likely to use, no matter what kind of character they are writing. In the upper right quadrant, we find the words that writers who are women are more likely to use. Writers who are women are more likely to write characters who sing, love, shift, sink into things, and burst into places. And lots of flinging! The lower left quadrant shows the words that writers who are men are more likely to use, for both male and female characters. Writers who are men are more likely to write characters who react, clutch, dive, shout, ducks, and emerge from places.
